
```{r}
PCdata = read.csv("prostate_cancer.csv")
print(PCdata)
```
```{r}
summary(PCdata)
```


```{r}
cor(PCdata)
```


```{r}
plot(PCdata$subject)
```
```{r}
# Scaling psa
LogPsa = log(PCdata$psa)
```

```{r}
boxplot(PCdata$psa)
```
```{r}
plot(PCdata$psa,PCdata$age)
```
```{r}
#Column Names
ColNames = colnames(PCdata)
ColNames
```
```{r}
#Relation between LogPsa and PCdata and PCdata$subject
plot(PCdata$subject, LogPsa)
Fit1 = lm(LogPsa~PCdata$subject, data = PCdata)
abline(Fit1)
```
```{r}
summary(Fit1)
```
```{r}
#Relation between LogPsa and PCdata and PCdata$cancervol
plot(PCdata$cancervol, LogPsa)
Fit2 = lm(LogPsa~PCdata$cancervol, data = PCdata)
abline(Fit2)
```
```{r}
summary(Fit2)
```
```{r}
#Relation between LogPsa and PCdata and PCdata$weight
plot(PCdata$weight, LogPsa)
Fit3 = lm(LogPsa~PCdata$weight, data = PCdata)
abline(Fit3)
```
```{r}
summary(Fit3)
```
```{r}
#Relation between LogPsa and PCdata and PCdata$age
plot(PCdata$age, LogPsa)
Fit4 = lm(LogPsa~PCdata$age, data = PCdata)
abline(Fit4)
```
```{r}
summary(Fit4)
```
```{r}
#Relation between LogPsa and PCdata and PCdata$benpros
plot(PCdata$benpros, LogPsa)
Fit5 = lm(LogPsa~PCdata$benpros, data = PCdata)
abline(Fit5)
```
```{r}
summary(Fit5)
```

```{r}
#Relation between LogPsa and PCdata and PCdata$vesinv
Vesinv = factor(PCdata$vesinv)
plot(PCdata$vesinv, LogPsa)
Fit6 = lm(LogPsa~PCdata$vesinv, data = PCdata)
abline(Fit6)
```
```{r}
summary(Fit6)
```

```{r}
#Relation between LogPsa and PCdata and PCdata$capspen
plot(PCdata$capspen, LogPsa)
Fit7 = lm(LogPsa~PCdata$capspen, data = PCdata)
abline(Fit7)

```

```{r}
summary(Fit7)
```

```{r}
#Relation between LogPsa and PCdata and PCdata$gleason
plot(PCdata$gleason, LogPsa)
Fit8 = lm(LogPsa~PCdata$gleason, data = PCdata)
abline(Fit8)
```

```{r}
summary(Fit8)
```
# One can conclude that carcervol, gleason, vesinv, benepros and capspen are significant and show considerable relationship with PSA level.
# To predict PSA we use different combinations of above predictors
```{r}
Fit9 = lm(LogPsa ~  PCdata$cancervol + factor(PCdata$vesinv) + PCdata$gleason + PCdata$capspen, data = PCdata )

```

```{r}
summary(Fit9)
```
# To  analyze changes in the model by including some of the predictors like PCdata$cancervol, factor(PCdata$vesinv), PCdata$gleason 
```{r}
Fit10 = lm(LogPsa ~  PCdata$cancervol + factor(PCdata$vesinv) + PCdata$gleason, data = PCdata )
```

```{r}
summary(Fit10)
```
```{r}
anova(Fit10, Fit9)
```
# Capsapen is not a significant predictor as pval is >=0.05
```{r}
# Using all significant predictors
FitAll = lm(LogPsa ~  PCdata$cancervol + factor(PCdata$vesinv) + PCdata$gleason + PCdata$benpros, data = PCdata )
```

```{r}
summary(FitAll)
```


```{r}
# Residual Plot
plot(fitted(FitAll), resid(FitAll))
abline(h=0)
```


```{r}
#QQ- Plot
qqnorm(resid(FitAll))
qqline(resid(FitAll))
```
# Question - Use the final model to predict the PSA level for a patient whose quantitative predictors are at the sample means of the variables and qualitative predictors are at the most frequent category.

# taking mean of quantitative and qualitative predictors
```{r}
CancervolMean = mean(PCdata$cancervol)
CancervolMean
```

```{r}
GleasonMean = mean(PCdata$gleason)
GleasonMean
```

```{r}
BenprosMean = mean(PCdata$benpros)
BenprosMean
```

```{r}
MfVesinv = names(which.max(table(factor(PCdata$vesinv))))
MfVesinv
```

```{r}
anova(Fit9, FitAll)
```


```{r}
anova(FitAll, Fit10)
```


```{r}
x1 = -0.65013
x2 = 0.06488
x3 = 0.68421
x4 = 0.33376
x5 = 0.09136
PredictingAns = exp(x1 + x2 * CancervolMean + x3 * 0 + x4* GleasonMean + x5 * BenprosMean)
PredictingAns
```

